Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/design.tex
typo
New figure

@@

\input{fig-dnsfull}
\paragraph{Rules.}
A Nail grammar consists of rules that assign a parser to a name. Rules are written as assignments,
such as \cc{ints = /*parser definition*/}, which defines a rule called \cc{ints}. As we will
describe later in \S\ref{s:dependent} and \S\ref{s:transforms}, rules can optionally consume parameters.
Rules can be invoked in a Nail grammar anywhere a parser can appear. Rule invocations act as though
the body of the rule had been substituted in the code. If parameters appear, they are passed by
reference.
\paragraph{Integers and constraints.}

@@

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.

>>>>

For example, Figure~\ref{fig:dns-full} shows an example grammar for DNS packets and the
corresponding data type and functions that Nail produces.

\input{fig-dnsfull}

@@

\paragraph{Parsing.}
\paragraph{Rules.}
A Nail grammar consists of rules that assign a parser to a name. Rules are written as assignments,
such as \cc{ints = /*parser definition*/}, which defines a rule called \cc{ints}. As we will
describe later in \S\ref{s:dependent} and \S\ref{s:transforms}, rules can optionally consume parameters.
Rules can be invoked in a Nail grammar anywhere a parser can appear. Rule invocations act as though
the body of the rule had been substituted in the code. If parameters appear, they are passed by
reference.
\paragraph{Integers and constraints.}

@@

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to be used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.
